Supplemental Materials, Methods and Results

### 2021-04-22 ms.Rmd
Updating script for the MS and supple

---
title: "Main Manuscript"
author: Whiting et al. 
date: "`r Sys.Date()`"
bibliography: refs.bib
csl: science.csl
output: 
  bookdown::word_document2:
    toc: no
    toc_depth: 6
    number_sections: true
    reference_docx: template.docx
  bookdown::html_document2:
    code_folding: hide
    number_sections: no
    toc: yes
    toc_depth: 6
    toc_float: yes
    bibliography: refs.bib
editor_options: 
  chunk_output_type: console
---

@@

```{r getlibrary, echo = FALSE, results = "hide"}
# load libraries
devtools::install_github("karthik/wesanderson")
pacman::p_load(lme4, lmerTest, ggplot2, lsmeans, emmeans, multcomp, dplyr, wesanderson, patchwork, ggarrange)
```

```{r displayModels, echo = FALSE, results = "hide"}
#Load data and clean a bit
Display_1 <- read.table("./data/Display_1.csv", 
                          header=TRUE, sep=",", dec=".", strip.white=TRUE)

@@

We conducted experiments manipulating both the social and predatory context chameleons encountered in their native Kenyan range, and the introduced Hawaiian range.

>>>>

---
title: "Evolution of a conspicuous dynamic visual signal in an introduced chameleon"
author: Whiting et al. 
date: "`r Sys.Date()`"
bibliography: refs.bib
csl: science.csl
output: 
  bookdown::word_document2:
    toc: no
    toc_depth: 6
    number_sections: true
    reference_docx: template.docx
  bookdown::html_document2:
    code_folding: hide
    number_sections: no
    toc: yes
    toc_depth: 6
    toc_float: yes
    bibliography: refs.bib
editor_options: 
  chunk_output_type: console
---

@@

```{r getlibrary, echo = FALSE, results = "hide"}
# load libraries
devtools::install_github("karthik/wesanderson")
pacman::p_load(lme4, lmerTest, ggplot2, lsmeans, emmeans, multcomp, dplyr, wesanderson, patchwork, latex2exp)

p_value <- function(x){
  if(x <= 0.0001) {tmp = "< 0.0001"}
  if(x <= 0.001 & x >= 0.0001) {tmp ="< 0.001"}
  if(x <= 0.01 & x >= 0.001) {tmp ="< 0.01"}
  if(x >= 0.01) {tmp =x}
  return(tmp)
}

```{r displayModels, echo = FALSE, results = "hide"}
#########################################################
# Male-male Competition Displays
#########################################################
#Load data and clean a bit
Display_1 <- read.table("./data/Display_1.csv", 
                          header=TRUE, sep=",", dec=".", strip.white=TRUE)

@@

# Display dl
    ConspicDisplayAC <- lmer(dL ~ SVL + Population + (1|ID), data=Display_1)
    summary(ConspicDisplayAC)
    anovaConspicDisplayAC <- anova(ConspicDisplayAC)

## Display dS
         ConspicDisplayCC <- lmer(dS ~ SVL + Population + (1|ID), data=Display_1)
    anovaConspicDisplayCC <- anova(ConspicDisplayCC)

#########################################################
# Courtship Displays
#########################################################

Courtship <- read.table("./data/Courtship_1.2.csv", 
                          header=TRUE, sep=",", dec=".", strip.white=TRUE)

# Courtship dl
ConspicCourtshipAC <- lmer(dL ~ SVL + Population  + (1|ID), data=Courtship)
courship_anovaAC <- anova(ConspicCourtshipAC)

# Courtship dS
  ConspicCourtshipCC <- lmer(dS ~ SVL + Population  + (1|ID), data=Courtship)
courship_anovaCC <- anova(ConspicCourtshipCC)
```

# Abstract
Rapid evolution frequently follows a significant change to an organism’s environment, such as during colonization of a novel habitat. Vertebrates, including Caribbean Anolis lizards and Galapagos finches, have demonstrated a remarkable capacity for morphological change of functional traits (limb length, beak size) on ecological time scales. Traits that are sexually selected can be similarly affected, although well-documented examples from wild populations are rare. The Jackson’s chameleon (*Chamaeleo x. jacksonii*) from East Africa was inadvertently introduced to the Hawaiian island of Oahu in 1972. In its native range, Jackson’s chameleons are preyed upon by a wide range of predators, including snakes and birds, which are thought to shape the dynamics of color change in chameleons. We took advantage of the Hawaiian introduction, an environment with only a few potential predators and therefore, very low predation pressure, to test for character release of conspicuous social color signals. To test this hypothesis, we measured color change in response to multiple social and predator stimuli in wild chameleons in both Hawai’i and Kenya. We used visual modelling of colour signals to estimate signal conspicuousness to both the chameleon and predator (bird, snake) visual systems. The Hawai’i and Kenya backgrounds were a similar color, but the major difference was in brightness: the Hawai’i background was darker. As a result, chameleons from both Kenya and Hawai’i were brighter against the Hawai’i background. However, Hawai’i males were more conspicuous (courtship, display) against their own background for some body regions (mainly gular), providing evidence for character release. Also, Hawai’i males were more conspicuous (courtship, display) to snake and bird predators against their own background. We suggest that relaxing natural selection can result in signal release in systems experiencing strong sexual selection.

# Introduction

When Darwin tackled the joint problems of speciation and evolutionary change through natural selection, he was of the view that evolution was a gradual process that took place over extended time periods. This view understandably persisted for at least another 120 years following the publication of On the Origin of Species (Darwin, 1859). We now have numerous examples of evolutionary change following natural selection in both the laboratory and wild, and not only in invertebrates with short generation times. Vertebrates, including Caribbean Anolis lizards and Galapagos finches, have demonstrated a remarkable capacity for morphological change of functional traits (limb length, beak size) on ecological time scales (e.g. @losos97). Furthermore, a far more recent development since Darwin’s seminal work on natural selection is the recognition that sexual selection can also drive significant changes in phenotype over short time intervals.

Conspicuous colour signals evolve because of the fitness advantage conferred to the signaller, and frequently becomes increasingly elaborate through a combination of male contest competition and female preference (e.g. runaway selection). However, trait exaggeration is typically halted by natural selection because there is a threshold beyond which conspicuousness is too costly. Evolution can respond to this selection pressure in a variety of ways that include shifting conspicuous signals to areas of the body that might be concealed to predators. For example, many conspicuous lizards have colourful throats and venters that they flash at conspecific receivers but which are not easily visible to raptors, which are a significant predator of lizards. Conversely, many species will balance the costs of sexual and natural selection and this is the case in Trinidadian guppies where populations living in predator-free streams are far more conspicuous than in predator-dense streams. These examples are from animals with static colour signals. A parallel solution that reduces the risk of exposure to predators is dynamic colour change because signals can be switched on and off relatively rapidly through neural or endocrine control. A wide range of invertebrates (e.g. cephalopods) and vertebrates (e.g. lizards and frogs) have convergently evolved this ability.

Unlike animals with static colour signals, we have a poor understanding of how animals with dynamic colour change respond to predation pressure and whether relaxing predation pressure will result in an increasingly conspicuous signal. Tackling this question in the wild is particularly difficult unless we can take advantage of unplanned changes to an organism’s environment such as during colonization of a novel habitat. Living organisms are occasionally translocated great distances by human action to environments far removed from their native range. These novel environments typically have a completely different suite of organisms, including predators, and offer a unique opportunity to study signal evolution in founder populations. Jackson’s chameleons (*Chamaeleo j. xanthopholus*) are just such a case. In 1972, a shipment of chameleons was sent from Kenya to the Hawaiian island of Oahu, destined for the pet trade. The animals arrived in poor condition and were left outdoors to recover, at which point they dispersed and became established on the island. On Oahu, the number of potential predators of chameleons is few (see methods), while in Kenya they are preyed upon by a wide range bird, snake and occasionally, mammal, predators.  This accidental introduction represents a unique opportunity to study the evolution of a dynamic visual signal by comparing native (Kenya) and introduced (Oahu) chameleons.

# Results

We conducted experiments manipulating both the social and predatory context chameleons encountered, in both their native Kenyan range and their introduced Hawaiian range, to test three hypotheses about colour signal evolution. First, we tested the hypothesis that relaxed predation pressure results in character release of a dynamic visual signal. Sexual selection favours more conspicious signals and these should evolve to be more conspicuous without predators. In suppor of this prediction, male display colouration exhibited in social contexts (i.e., male-male contests and courtship) was more conspicuous to a conspecific in Hawaii compared with Kenya (**Male-Male Contests**: Acromatic ($dl$); $F_{`r anovaConspicDisplayAC$NumDF[2]`,`r anovaConspicDisplayAC$DenDF[2]`}$ = `r anovaConspicDisplayAC[5][2,]`, p = `r p_value(anovaConspicDisplayAC[6][2,])`; Chromatic ($dS$): $F_{`r anovaConspicDisplayCC$NumDF[2]`,`r anovaConspicDisplayCC$DenDF[2]`}$ = `r anovaConspicDisplayCC[5][2,]`, p = `r p_value(anovaConspicDisplayCC[6][2,])`; **Courtship displays**: Acromatic ($dl$); $F_{`r courship_anovaAC$NumDF[2]`,`r courship_anovaAC$DenDF[2]`}$ = `r courship_anovaAC[5][2,]`, p = `r p_value(courship_anovaAC[6][2,])`; Chromatic ($dS$): $F_{`r courship_anovaCC$NumDF[2]`,`r courship_anovaCC$DenDF[2]`}$ = `r courship_anovaCC[5][2,]`, p = `r p_value(courship_anovaCC[6][2,])`), and this was true across all body regions measured (See Supplemental Materials, Table S1).

Specifically, we tested the following predictions: 1.) display colouration used in male-male contests and courtship will be more conspicuous to a conspecific in Hawaii than Kenya; 2.) display colouration used in response to an encounter with a bird and snake predator will be more conspicuous to both predator types in Hawai’i than Kenya. 3.) under character release, males will have greater capacity to change colour from a subordinate to a dominant state in Hawai’i compared to Kenya.

We also tested the hypothesis that sensory drive and local adaptation are responsible for driving display coloration. Specifically, we predicted that chameleon display colouration in each population would be more conspicuous within its own signaling environment compared to the other population’s signaling environment. For example, Hawaiian chameleons were historically found in Kenya but under sensory drive and local adaptation they are predicted to be more conspicuous in their current signaling environment, Hawai’i. Likewise, Kenyan chameleons have no history in Hawai’i and are therefore predicted to be more conspicuous within their current signaling environment, Kenya.

### 2021-04-22 supp.Rmd
Updating script for the MS and supple

---
title: "Supplemental Materials, Methods and Results"
author: Whiting et al. 
date: "`r Sys.Date()`"
bibliography: refs.bib
csl: science.csl
output: 
  bookdown::html_document2:
    code_folding: hide
    number_sections: no
    toc: yes
    toc_depth: 6
    toc_float: yes
    bibliography: refs.bib
  bookdown::word_document2:
    toc: no
    toc_depth: 6
    number_sections: true
    reference_docx: template.docx
editor_options: 
  chunk_output_type: console
---

```{r display}
#Load data and clean a bit
Display_1 <- read.table("../data/Display_1.csv", 
                          header=TRUE, sep=",", dec=".", strip.white=TRUE)

@@

# Fit the model that esatimtes changes across body regions
ConspicDisplayAC <- lmer(dL ~ SVL + Population + BodyRegion + Background 
                         + Population:Background + Population:BodyRegion + (1|ID), data=Display_1)
Display_1$PopBRInt <- interaction(Display_1$Population,Display_1$BodyRegion)
ConspicDisplayAC2 <- lmer(dL ~ PopBRInt + (1|ID), data=Display_1)
summary(glht(ConspicDisplayAC2, linfct = mcp(PopBRInt = c("Hawaii.gular - Kenya.gular = 0","Hawaii.midflank - Kenya.midflank = 0", "Hawaii.topflank - Kenya.topflank = 0", 
                                                          "Hawaii.tailbase - Kenya.tailbase = 0" ))))
```

>>>>

---
title: "Supplemental Materials, Methods and Results"
author: Whiting et al. 
date: "`r Sys.Date()`"
bibliography: refs.bib
csl: science.csl
output: 
  bookdown::word_document2:
    toc: no
    toc_depth: 6
    number_sections: true
    reference_docx: template.docx
  bookdown::html_document2:
    code_folding: hide
    number_sections: no
    toc: yes
    toc_depth: 6
    toc_float: yes
    bibliography: refs.bib
editor_options: 
  chunk_output_type: console
---
```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE, cache = TRUE, message = FALSE, warning = FALSE, tidy = TRUE, fig.width = 10)
## numbers >= 10^5 will be denoted in scientific notation,      ## numbers >= 10^5 will be denoted in scientific notation,
  ## and rounded to 2 digits      ## and rounded to 2 digits
  options(digits = 2)
```

```{r getlibrary, echo = FALSE, results = "hide"}
# load libraries
devtools::install_github("karthik/wesanderson")
pacman::p_load(lme4, lmerTest, ggplot2, lsmeans, emmeans, multcomp, dplyr, wesanderson, patchwork, pander, kableExtra, flextable)
```

```{r display, results = "hide"}

#########################################################
# Male-male Competition Displays
#########################################################
#Load data and clean a bit
Display_1 <- read.table("./data/Display_1.csv", 
                          header=TRUE, sep=",", dec=".", strip.white=TRUE)

@@

# Fit the model that esatimtes changes across body regions
ConspicDisplayAC <- lmer(dL ~ SVL + Population + BodyRegion + Background 
                         + Population:Background + Population:BodyRegion + (1|ID), data=Display_1)

# Fit model for linear hypothesis tests
Display_1$PopBRInt <- interaction(Display_1$Population,Display_1$BodyRegion)
ConspicDisplayAC2 <- lmer(dL ~ PopBRInt + (1|ID), data=Display_1)

result1 = glht(ConspicDisplayAC2, linfct = mcp(PopBRInt = c("Hawaii.gular - Kenya.gular = 0",
                                                            "Hawaii.midflank - Kenya.midflank = 0",     
                                                            "Hawaii.topflank - Kenya.topflank = 0", 
                                                             "Hawaii.tailbase - Kenya.tailbase = 0" )))

## Display - Chromatic contrast (CC or dS)
## just this next section has Drew's code, which averages the backround (Leaf_B1, Leaf_B2, Leaf_T1, Leaf_T2, Stem1, Stem2) for each lizard body region measurement.
## This is the full model; however, we do not need background because the way the data is set up R is taking an average. See next model (background dropped)

# Fit the model that esatimtes changes across body regions
  ConspicDisplayCC <- lmer(dS ~ SVL + Population + BodyRegion + Background 
                         + Population:Background + Population:BodyRegion + (1|ID), data=Display_1)
Display_1$PopBRInt <- interaction(Display_1$Population,Display_1$BodyRegion)

# Fit model for linear hypothesis tests
ConspicDisplayCC2 <- lmer(dS ~ PopBRInt + (1|ID), data=Display_1)
summary(glht(ConspicDisplayCC2, linfct = mcp(PopBRInt = c("Hawaii.gular - Kenya.gular = 0",
                                                          "Hawaii.midflank - Kenya.midflank = 0", 
                                                          "Hawaii.topflank - Kenya.topflank = 0", 
                                                          "Hawaii.tailbase - Kenya.tailbase = 0" ))))

#########################################################
# Courtship Displays
#########################################################

Courtship <- read.table("./data/Courtship_1.2.csv", 
                          header=TRUE, sep=",", dec=".", strip.white=TRUE)

# Courtship - Chromatic dl
ConspicCourtshipAC <- lmer(dL ~ SVL + Population + BodyRegion + Background 
                           + Population:Background + Population:BodyRegion + (1|ID), data=Courtship)

Courtship$PopBRInt <- interaction(Courtship$Population,Courtship$BodyRegion)
ConspicCourtshipAC2 <- lmer(dL ~ PopBRInt + (1|ID), data=Courtship)
summary(glht(ConspicCourtshipAC2, linfct = mcp(PopBRInt = c("Hawaii.gular - Kenya.gular = 0","Hawaii.midflank - Kenya.midflank = 0", "Hawaii.topflank - Kenya.topflank = 0", 
                                                            "Hawaii.tailbase - Kenya.tailbase = 0" ))))

ConspicCourtshipAC <- lmer(dL ~ SVL + Population + BodyRegion +  
                             + Population:BodyRegion + (1|ID), data=Courtship)
anova(ConspicCourtshipAC)
ranova(ConspicCourtshipAC)

# Courtship - Chromatic dS
ConspicCourtshipCC <- lmer(dS ~ SVL + Population + BodyRegion + Background 
                           + Population:Background + Population:BodyRegion + (1|ID), data=Courtship)
Courtship$PopBRInt <- interaction(Courtship$Population,Courtship$BodyRegion)
ConspicCourtshipCC2 <- lmer(dS ~ PopBRInt + (1|ID), data=Courtship)
summary(glht(ConspicCourtshipCC2, linfct = mcp(PopBRInt = c("Hawaii.gular - Kenya.gular = 0","Hawaii.midflank - Kenya.midflank = 0", "Hawaii.topflank - Kenya.topflank = 0", 
                                                            "Hawaii.tailbase - Kenya.tailbase = 0" ))))

```

# Materials and Methods

## Study area and collection of chameleons

We collected most chameleons at night by spotlighting, and a small proportion of individuals during the day. When chameleons were beyond reach, we used 4-m extensible poles that chameleons could be encouraged to step on to, before lowering them to the ground. We then placed them in cotton bags with vegetation to cling to, before returning them to the lab. Field work was conducted in Hawai’i during January-February 2006 and in Kenya during 5-13 April 2006. In Hawai’i, chameleons were collected from a single population in the Manoa Valley, Oahu, accessible along Tantalus Drive at an elevation of ca. x-x. The vegetation in this area consisted of closed-canopy, mid-elevation tropical rain forest, with extensive vines and undergrowth. Most of the plants in this area were nonnative, and chameleons also occurred in hedge-grows and stands of bamboo. The area experiences high annual rainfall (mean: xx). In Kenya, field work was conducted near the foothills of Mt. Kenya, close to the town of Runyenjes. The area is partially cleared for agriculture, leaving small stands of forest. The vegetation was a mix of native trees and shrubs interspersed with exotic species.

## Behaviour trials

In order to quantify display colouration we staged encounters between conspecifics (male-male and male-female) and model (bird and snake) predators and measured their subsequent display colouration (details below). All chameleons were used in both predator and social trials although in some cases we were unable to quantify all social signals for a particular individual. We conducted all conspecific-social trials first, in case anti-predator trials unduly influenced their social interactions. Behavioural trials were conducted during the chameleons’ natural activity period (09:00-16:00 h) beginning the day following capture and continuing over a 2-3 day period. We erected a frame consisting of branches from the chameleons’ environment that were tied together in a triangle and which sat atop three vertical branches that formed a stand. This structure was about 1.5 m high and each arm was approximately 60 cm. The triangular setup allowed chameleons to display at a comfortable distance and also to escape from aggressive interactions, particularly during male-male trials. All trials were conducted outdoors, but in the shade under the cover of a roof, with vegetation nearby, to simulate their natural environment. The signalling environment was therefore the same for all animals.

We staged trials between males to elicit dominant and subordinate displays and between males and females to elicit courtship displays. This consisted of placing two chameleons at a comfortable distance at which point they typically responded to the conspecific’s presence by rapidly changing colour and behaviour. In male-male trials both individuals would adopt a lemon-yellow display coloration (Fig. x) and advance towards each other. This would be accompanied by head shakes and would lead to horn-locking if males were not obviously asymmetric. Once dominance was settled, the subordinate would turn brown and flee. In male-female (courtship) trials, males would turn the same lemon-yellow and approach the female while head shaking and rocking. The day following social trials we presented each chameleon with a snake and bird model predator (separately). Lizards were drawn at random and the order of presentation (snake or bird first) was random. Both trials were conducted on the same day but were separated by at least three hours. A trial began when a chameleon was removed from its cloth bag and placed on the triangular stand. At this point the lizard was in a neutral colour state. In the case of the snake model, one of us slowly moved the model snake towards the chameleon from both above and below it, without ever contacting the chameleon. In the case of the bird trials, the bird was attached to a x cm wooden pole and was ‘flown’ past the chameleon from above and below it. Trials lasted no more than 2-min and we scored whether the chameleon flipped to the opposite side of the branch, which is a classic anti-predator behaviour by chameleons. Once chameleons changed colour, we quantified their spectral reflectance following the same procedure described for social trials. We also conducted seven trials with a just a branch with no predator attached, as a control for the model predator. The snake model was moulded from a dead boomslang (Dispholidus typus) and painted by a professional artist to resemble a typical green form of this species (previously used in Stuart-Fox…). The bird was ….

## Colour measurements, habitat background and irradiance

During all behaviour trials, we measured the colour of each body region (Fig. x) once only, because chameleons change colour rapidly and we had to reduce the handling stress to the animal. Patches were measured in random sequence to avoid any bias of order. When a chameleon had completely changed colour (to a human observer) and was also performing typical behaviour associated with their display (e.g., head shakes, swaying, gaping, rapid approach or flee) we lightly restrained it with one hand, without removing it from its perch, and measured spectral reflectance using a 1.2 m bifurcated probe connected to an Ocean Optics USB-2000 optic spectrophotometer and a PX2 light source. We used a custom-made probe-holder which we placed in contact with the animal at a standard angle (45; @RN2) and distance (5 mm), thereby excluding ambient light. All measurements were relative to a dark, and a certified 99% white reflectance standard. When chameleons started to change colour in response to our handling we stopped measuring colour and allowed them to continue a social trial before continuing to measure spectral reflectance. In the case of a predator trial we would once again present them with the predator model until they returned to their anti-predator display. This system worked effectively because chameleons readily responded to social and anti-predator stimuli and quickly returned to natural behaviour following handling.

We quantified the background against which chameleons signal by measuring the spectral reflectance of vegetation in their signalling environment. This included 1.) the upper surface of leaves; 2.) the underside of leaves; and 3.) branches. We also measured the habitat light environment by recording irradiance in the chameleons environment.

## Visual modelling

# Supplemental Results

```{r tableS1}
summary(result1)
```

```{FigS1, fig.width = 5, fig.height = 10, fig.caption = "test"}

#Making a point plot with error bars split by body size and population 
#Compute raw means and standard errors for body part and population for dS and assigned this data into Display_plot_dS_dat
Display_plot_dS_dat <- Display_1 %>% #data for dS Chromatic constrast
  group_by(Population, BodyRegion) %>% 
  summarise(Mean = mean(dS, na.rm = T), 
            SE = sd(dS)/sqrt(length(unique(ID))),
            Upper = Mean + 1.96*SE,
            Lower = Mean - 1.96*SE)

Display_plot_dL_dat <- Display_1 %>% #data for dL Achromatic contrast
  group_by(Population, BodyRegion) %>% 
  summarise(Mean = mean(dL, na.rm = T), 
            SE = sd(dL)/sqrt(length(unique(ID))),
            Upper = Mean + 1.96*SE,
            Lower = Mean - 1.96*SE)

#Plotting Chromatic contrast (dS)
p1 <- ggplot(Display_plot_dS_dat, aes(x = Population, y = Mean, group = BodyRegion, color = BodyRegion)) +
  geom_point(size = 3) +
  geom_line() +
  geom_errorbar(aes(ymin = Lower, ymax = Upper), width = 0) + 
  scale_color_manual(values = wes_palette("Cavalcanti1")) + #Change color palette here see: https://github.com/karthik/wesanderson
  xlab("") + 
  ylab(TeX("Chromatic contrast (JND)")) +
  theme_bw() +
  theme(legend.position = "none",
    panel.grid.major = element_blank(), 
    panel.grid.minor = element_blank(),
    axis.text=element_text(size=18),
    axis.title=element_text(size=20,face="bold"),
    legend.text =element_text(size = 12),
    legend.title =element_text(size = 12, face = "bold"))

#Plotting Achromatic contrast (dL)
p2 <- ggplot(Display_plot_dL_dat, aes(x = Population, y = Mean, group = BodyRegion, color = BodyRegion)) +
  geom_point(size = 3) +
  geom_line() +
  geom_errorbar(aes(ymin = Lower, ymax = Upper), width = 0) + 
  scale_color_manual(values = wes_palette("Cavalcanti1")) + #Change color palette here see: https://github.com/karthik/wesanderson
  xlab("") + 
  ylab(TeX("Achromatic contrast (JND)")) +
  theme_bw() +
  theme(#legend.position = "none",
    panel.grid.major = element_blank(), 
    panel.grid.minor = element_blank(),
    axis.text=element_text(size=18),
    axis.title=element_text(size=20,face="bold"),
    legend.text =element_text(size = 12),
    legend.title =element_text(size = 12, face = "bold"))

#Making a point plot with error bars split by body size and population 
#Compute raw means and standard errors for body part and population for dS and assigned this data into Display_plot_dS_dat
Courtship_plot_dS_dat <- Courtship %>% #data for dS Chromatic constrast
  group_by(Population, BodyRegion) %>% 
  summarise(Mean = mean(dS, na.rm = T), 
            SE = sd(dS)/sqrt(length(unique(ID))),
            Upper = Mean + 1.96*SE,
            Lower = Mean - 1.96*SE)

Courtship_plot_dL_dat <- Courtship %>% #data for dL Achromatic contrast
  group_by(Population, BodyRegion) %>% 
  summarise(Mean = mean(dL, na.rm = T), 
            SE = sd(dL)/sqrt(length(unique(ID))),
            Upper = Mean + 1.96*SE,
            Lower = Mean - 1.96*SE)

#Plotting Chromatic contrast (dS)
p3 <- ggplot(Courtship_plot_dS_dat, aes(x = Population, y = Mean, group = BodyRegion, color = BodyRegion)) +
  geom_point(size = 3) +
  geom_line() +
  geom_errorbar(aes(ymin = Lower, ymax = Upper), width = 0) + 
  scale_color_manual(values = wes_palette("Cavalcanti1")) + #Change color palette here see: https://github.com/karthik/wesanderson
  xlab("") + 
  ylab(TeX("Chromatic contrast (JND)")) +
  theme_bw() +
  theme(legend.position = "none",
    panel.grid.major = element_blank(), 
    panel.grid.minor = element_blank(),
    axis.text=element_text(size=18),
    axis.title=element_text(size=20,face="bold"),
    legend.text =element_text(size = 12),
    legend.title =element_text(size = 12, face = "bold"))

#Plotting Achromatic contrast (dL)
p4 <- ggplot(Courtship_plot_dL_dat, aes(x = Population, y = Mean, group = BodyRegion, color = BodyRegion)) +
  geom_point(size = 3) +
  geom_line() +
  geom_errorbar(aes(ymin = Lower, ymax = Upper), width = 0) + 
  scale_color_manual(values = wes_palette("Cavalcanti1")) + #Change color palette here see: https://github.com/karthik/wesanderson
  xlab("") + 
  ylab(TeX("Achromatic contrast (JND)")) +
  theme_bw() +
  theme(legend.position = "none",
    panel.grid.major = element_blank(), 
    panel.grid.minor = element_blank(),
    axis.text=element_text(size=18),
    axis.title=element_text(size=20,face="bold"),
    legend.text =element_text(size = 12),
    legend.title =element_text(size = 12, face = "bold"))

p1 + p2 + p3 + p4 + plot_annotation(tag_levels = c('A', 'B', 'C', 'D')) & theme(plot.tag = element_text(face = 'bold', size=20))

```

# References
